Digital Analysis of Paintings

### 2014-04-29 paper.tex
Make a start on paper 11.

@@

>>>>

% TODO Again, another complex one :-(

@@

Analysis of texture can also be performed with the help of a set of small
patches, or textons, relating to the texture of the image. An interesting
approach is to learn a variety of these textons from example images and then
look at a histogram of the frequencies of these textons on the images to
classify\cite{van2010texton}.

Segmentation of brushstrokes is, understandably, difficult - especially
digitally where the image is usually only two dimensional.
